Field training 02 - Leaf traits measurements

### 2023-06-13 submission_2/submission_2.qmd
add scan vs cam plot
Updates report & new images path

![Table with formulas to convert measured SPAD pigment values to chlorophyll per area values.](SPAD_conversion_table.png "Table with formulas to convert measured SPAD pigment values to chlorophyll per area values.")

@@

![Variation of the different equations used to convert the measured SPAD-values to real chlorophyll values.](SPAD_conversion_variation.png "Variation of the different equations used to convert the measured SPAD-values to real chlorophyll values.")

@@

@@

To calculate the biomass of the sheets, we now had to determine the dry weight of the sheets. To do this, we put the leaves back in the paper bag, and put them in the drying oven at 50 - 55 °C. The samples were dried for 72h. Then we measured the dry weight and noted the values. Finally we calculated the ratio of dry weight to leaf area in mg/cm², which is the Leaf mass per Aria (LMA).  
## Comparison to LEDA Database

Another task was to compare our LMA values with those from the LEDA database. There, the values were only available as SLA. So we had to convert them into LMA first. The result can be seen in the plots in the appendix. If several values were available for one plant, we calculated the mean value. For two plants no values were available in the LEDA database. Overall, our values are slightly higher than those in the database, but are very similar overall.

@@

 $$
 EWT = \frac{fresh\: weight\: [mg]-dry\: weight\: [mg]}{1000\:\frac{mg}{cm^{3}}\; \; leaf\: area\: [cm^{2}]}
 $$ {#eq-EWT}

>>>>

![Table with formulas to convert measured SPAD pigment values to chlorophyll per area values.](imgs/SPAD_conversion_table.png "Table with formulas to convert measured SPAD pigment values to chlorophyll per area values.")

@@

![Variation of the different equations used to convert the measured SPAD-values to real chlorophyll values.](imgs/SPAD_conversion_variation.png "Variation of the different equations used to convert the measured SPAD-values to real chlorophyll values."){width=80%}

@@

![Scatterplot comparing results of Leaf area from the scanner vs Leaf area out of camera photos.](imgs/leaf-area_scan_vs_cam.png "Scatterplot comparing results of Leaf area from the scanner vs Leaf area out of camera photos."){width=70%}

@@

To calculate the biomass of the sheets, we now had to determine the dry weight of the sheets. To do this, we put the leaves back in the paper bag, and put them in the drying oven at 50 - 55 °C. The samples were dried for 72h. Then we measured the dry weight and noted the values. Finally we calculated the ratio of dry weight to leaf area in mg/cm², which is the Leaf mass per Aria (LMA).

## Comparison to LEDA Database

Another task was to compare our LMA values with those from the LEDA database (See Figure 2 in this section). There, the values were available as mean SLA, so we converted them into LMA first. If several values were available for one plant, we calculated the mean value. For two plants no values were available in the LEDA database. Overall, our values are slightly higher than those in the database, but are very similar overall.

![Comparison of our LMA values (red) to values from the LEDA database (blue)](imgs/leda_lma_comparison.png)

@@

 $$
 EWT = \frac{fresh\: weight\: [mg]-dry\: weight\: [mg]}{1000\:\frac{mg}{cm^{3}}\; \; leaf\: area\: [cm^{2}]}
 $$ {#eq-EWT}
{{< pagebreak >}}
